---
title: "Portfolio5"
author: "Fei Xie"
date: "5/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#COVID World Map

The aim of this portfolio is to compare the developing trend of COVID cases in country-wide and continent-wide, and draw a world map of COVID.

```{r COVIDdata}
library(lubridate)
library(dplyr)
library(tidyverse)
library(rworldmap)

COVID <- read.csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv", na.strings = "", fileEncoding = "UTF-8-BOM", stringsAsFactors = F)
```

```{r description}
glimpse(COVID)
COVID %>%
  count(countriesAndTerritories)
```

There are 12 columns and 61900 rows, recording the accumulative covid cases in 214 countries across the world.

##Developing trend of COVID cases in the US
```{r US_trend}
data_US <- COVID %>%
  filter (countriesAndTerritories == "United_States_of_America")

data_US %>%
  group_by(month) %>%
  summarize(cases = sum(cases)) %>%
  ggplot(aes (
    x = month,
    y = cases)) +
  geom_path(color="Red")+
  labs(
    title = "the developing trend of COVID cases in the United States of America (2019/12/31-2020/12/14)",
    x = "Date",
    y = "Cases"
  ) 
```


##Developing trend of COVID cases and death number in the US
```{r US_death_trend}
data_US%>%
  group_by(month) %>%
  summarize(cases = sum(cases), deaths = sum(deaths)) %>%
  
  ggplot(aes (
    x = month)) +
  geom_path(aes(y = deaths/100), color="Blue")+
  geom_path(aes(y = cases/1000), color = "Red")+
  scale_y_continuous(name = "Deaths/100", sec.axis = sec_axis(~.*10, name = "COVID cases/1000"))+
  theme(
    axis.title.y = element_text(color = "Blue", size=13),
    axis.title.y.right = element_text(color = "Red", size=13)
  ) +
  labs(
    title = "the developing trend of COVID cases in the United States of America",
    subtitle = "from  2019/12/31 to 2020/12/14",
    x = "Month/2020",
    y = "Cases"
  ) 
```

##Developing trend of COVID cases and death number in China
```{r China_death_trend}
data_China <- COVID %>%
    filter (countriesAndTerritories == "China")

data_China%>%
  group_by(month) %>%
  summarize(cases = sum(cases), deaths = sum(deaths)) %>%
  
  ggplot(aes (
    x = month)) +
  geom_path(aes(y = deaths/100), color="Blue")+
  geom_path(aes(y = cases/1000), color = "Red")+
  scale_y_continuous(name = "Deaths/100", sec.axis = sec_axis(~.*10, name = "COVID cases/1000"))+
  theme(
    axis.title.y = element_text(color = "Blue", size=13),
    axis.title.y.right = element_text(color = "Red", size=13)
  ) +
  labs(
    title = "the developing trend of COVID cases in China",
    subtitle = "from  2019/12/31 to 2020/12/14",
    x = "Month/2020",
    y = "Cases"
  ) 

```

#The latest map of acculmulative COVID cases (2020/12/14)

```{r the_latest_data}
data_late <- COVID %>%
  filter (dateRep == "14/12/2020")
```

```{r the_latest_barplot}
barplotCountryData()

data(data_late, envir = environment(), package = "rworldmap")

barplotCountryData(data_late,
                   nameColumnToPlot = "cases",
                   nameCountryColumn = "countryterritoryCode",
                   maptitle = "the ranking of the COVID cases across countries (2020/12/14)")

```

#The World map of  the latest COVID cases (2020/12/14)
```{r the_latest_map}
mapCountryData()

data(data_late, envir = environment(), package = "rworldmap")
sPDF <- joinCountryData2Map(data_late
              , nameJoinColumn = "countryterritoryCode")

mapCountryData( sPDF
              , nameColumnToPlot="cases" 
              )
  missingCountryCol = gray(.8)
```

#The Eorupean map of the latest COVID cases (2020/12/14)
```{r the_latest_map}
data_Europe <- data_late %>%
  filter (continentExp == "Europe")

mapCountryData()

data(data_Europe,envir = environment(), package = "rworldmap")
sPDF <- joinCountryData2Map(data_Europe
              , nameJoinColumn = "countryterritoryCode")

mapCountryData( sPDF
              , nameColumnToPlot="cases" ,
              mapRegion = "Europe"
              )
  missingCountryCol = gray(.8)
```